---
title: "Wastewater data summary stats"
author: "Leah Lariscy"
output: html_document
---

# Load packages

```{r}
library(tidyverse)
library(here)
library(tsibble)
library(ggpubr)
```

# Load data

```{r}
#cq data (not summarized)
cq_unsum <- readRDS(here("data/processed_data/qpcr_plant_all.rds"))

#viral load data (avg technical reps)
viral_load_sum_tech_reps <- readRDS(here("data/processed_data/wastewater/viral_load_tech_rep_avg.rds"))

#viral load data (daily avg)
viral_load_sum_daily <- readRDS(here("data/processed_data/wastewater/viral_load_daily_avg.rds"))

#viral load data (weekly avg)
viral_load_sum_weekly <- readRDS(here("data/processed_data/wastewater/viral_load_weekly_avg.rds")) %>% 
  select(c(week,A_N1,A_N2,B_N1,B_N2,C_N1,C_N2))

#detection frequency data (daily total)
detection_freq_unsum <- readRDS(here("data/processed_data/wastewater/detection_frequency_daily.rds")) %>% 
  mutate(pos_rate = n_pos/n)

#summarized detection frequency data (weekly total)
detection_freq_sum <- readRDS(here("data/processed_data/wbe_covid_n6_week.rds")) %>% 
  select(c(week,A_N1_POS,A_N2_POS,B_N1_POS,B_N2_POS,C_N1_POS,C_N2_POS))

#load clinical timeseries figures
test_admin <- readRDS(here("figures/timeseries/test_admin.rds"))
cases_reported <- readRDS(here("figures/timeseries/cases_reported.rds"))
```

# Summarize

## Total collection dates

```{r}
# Counting the number of unique collection dates
collection_dates <- length(unique(viral_load_sum_daily$date))

# Display the result
print(paste("Number of collection dates:", collection_dates))
```

## Total collections

```{r}
total_collections <- viral_load_sum_daily %>% n_groups()
print(paste("Number of collections:",total_collections))
```

```{r}
viral_load_sum_daily %>% 
  ungroup() %>% 
  filter(facility=="A") %>% 
  group_by(date) %>% 
  n_groups()

viral_load_sum_daily %>% 
  ungroup() %>% 
  filter(facility=="B") %>% 
  group_by(date) %>% 
  n_groups()

viral_load_sum_daily %>% 
  ungroup() %>% 
  filter(facility=="C") %>% 
  group_by(date) %>% 
  n_groups()
```

## Total detections

```{r}
#count number of total biological replicates
total_bio_reps <- cq_unsum %>% 
  group_by(date,facility,target,biological_replicate) %>% 
  n_groups()

print(total_bio_reps)

#count number of biological replicates with at least one detectable reaction
contains_detection <- cq_unsum %>%
  group_by(date,facility,target,biological_replicate) %>%
  summarize(contains_detection = any(nondetect == "detect" & ct_lod == "detectable"))

total_detections <- contains_detection %>% 
  filter(contains_detection == "TRUE") %>% 
  nrow()

print(total_detections)

#count number of biological replicates with no detectable reactions
total_nondetections <- contains_detection %>% 
  filter(contains_detection == "FALSE") %>% 
  nrow()

print(total_nondetections)

#calculate total detection rate
total_detection_freq <- total_detections/total_bio_reps

print(total_detection_freq)
```

## N1 detections

```{r}
#count number of total n1 biological replicates
total_bio_reps_n1 <- cq_unsum %>% 
  filter(target == "N1") %>% 
  group_by(date,facility,target,biological_replicate)

print(n_groups(total_bio_reps_n1))

#count number of biological replicates with at least one detectable reaction
contains_detection_n1 <- cq_unsum %>%
  filter(target == "N1") %>% 
  group_by(date,facility,target,biological_replicate) %>%
  summarize(contains_detection = any(nondetect == "detect" & ct_lod == "detectable"))

total_detections_n1 <- contains_detection_n1 %>% 
  filter(contains_detection == "TRUE") %>% 
  nrow()

print(total_detections_n1)

#count number of biological replicates with no detectable reactions
total_nondetections_n1 <- contains_detection_n1 %>% 
  filter(contains_detection == "FALSE") %>% 
  nrow()

print(total_nondetections_n1)

#calculate total detection rate
total_detection_freq_n1 <- total_detections_n1/n_groups(total_bio_reps_n1)

print(total_detection_freq_n1)
```

### Y1

```{r}
#count number of total n1 biological replicates
total_bio_reps_n1_y1 <- cq_unsum %>% 
  filter(target == "N1" & date <= '2021-06-30') %>% 
  group_by(date,facility,target,biological_replicate)

print(n_groups(total_bio_reps_n1_y1))

#count number of biological replicates with at least one detectable reaction
contains_detection_n1_y1 <- cq_unsum %>%
  filter(target == "N1" & date <= '2021-06-30') %>% 
  group_by(date,facility,target,biological_replicate) %>%
  summarize(contains_detection = any(nondetect == "detect" & ct_lod == "detectable"))

total_detections_n1_y1 <- contains_detection_n1_y1 %>% 
  filter(contains_detection == "TRUE") %>% 
  nrow()

print(total_detections_n1_y1)

#calculate total detection rate
total_detection_freq_n1_y1 <- 
  total_detections_n1_y1/n_groups(total_bio_reps_n1_y1)

print(total_detection_freq_n1_y1)

#count number of reps with all detectable reactions
cq_unsum %>%
  filter(target == "N1" & date <= '2021-06-30') %>% 
  group_by(date,facility,target,biological_replicate) %>%
  summarize(contains_detection = all(nondetect == "detect" & ct_lod == "detectable")) %>% 
  filter(contains_detection == "TRUE") %>% 
  nrow()
```

### Y2

```{r}
#count number of total n1 biological replicates
total_bio_reps_n1_y2 <- cq_unsum %>% 
  filter(target == "N1" & date > '2021-06-30') %>% 
  group_by(date,facility,target,biological_replicate)

print(n_groups(total_bio_reps_n1_y2))

#count number of biological replicates with at least one detectable reaction
contains_detection_n1_y2 <- cq_unsum %>%
  filter(target == "N1" & date > '2021-06-30') %>% 
  group_by(date,facility,target,biological_replicate) %>%
  summarize(contains_detection = any(nondetect == "detect" & ct_lod == "detectable"))

total_detections_n1_y2 <- contains_detection_n1_y2 %>% 
  filter(contains_detection == "TRUE") %>% 
  nrow()

print(total_detections_n1_y2)

#calculate total detection rate
total_detection_freq_n1_y2 <- 
  total_detections_n1_y2/n_groups(total_bio_reps_n1_y2)

print(total_detection_freq_n1_y2)

#count number of reps with all detectable reactions
cq_unsum %>%
  filter(target == "N1" & date > '2021-06-30') %>% 
  group_by(date,facility,target,biological_replicate) %>%
  summarize(contains_detection = all(nondetect == "detect" & ct_lod == "detectable")) %>% 
  filter(contains_detection == "TRUE") %>% 
  nrow()
```

## N2 detections

```{r}
#count number of total n2 biological replicates
total_bio_reps_n2 <- cq_unsum %>% 
  filter(target == "N2") %>% 
  group_by(date,facility,target,biological_replicate)

print(n_groups(total_bio_reps_n2))

#count number of biological replicates with at least one detectable reaction
contains_detection_n2 <- cq_unsum %>%
  filter(target == "N2") %>% 
  group_by(date,facility,target,biological_replicate) %>%
  summarize(contains_detection = any(nondetect == "detect" & ct_lod == "detectable"))

total_detections_n2 <- contains_detection_n2 %>% 
  filter(contains_detection == "TRUE") %>% 
  nrow()

print(total_detections_n2)

#count number of biological replicates with no detectable reactions
total_nondetections_n2 <- contains_detection_n2 %>% 
  filter(contains_detection == "FALSE") %>% 
  nrow()

print(total_nondetections_n2)

#calculate total detection rate
total_detection_freq_n2 <- total_detections_n2/n_groups(total_bio_reps_n2)

print(total_detection_freq_n2)
```

### Y1

```{r}
#count number of total n2 biological replicates
total_bio_reps_n2_y1 <- cq_unsum %>% 
  filter(target == "N2" & date <= '2021-06-30') %>% 
  group_by(date,facility,target,biological_replicate)

print(n_groups(total_bio_reps_n2_y1))

#count number of biological replicates with at least one detectable reaction
contains_detection_n2_y1 <- cq_unsum %>%
  filter(target == "N2" & date <= '2021-06-30') %>% 
  group_by(date,facility,target,biological_replicate) %>%
  summarize(contains_detection = any(nondetect == "detect" & ct_lod == "detectable"))

total_detections_n2_y1 <- contains_detection_n2_y1 %>% 
  filter(contains_detection == "TRUE") %>% 
  nrow()

print(total_detections_n2_y1)

#calculate total detection rate
total_detection_freq_n2_y1 <- 
  total_detections_n2_y1/n_groups(total_bio_reps_n2_y1)

print(total_detection_freq_n2_y1)

#count number of reps with all detectable reactions
cq_unsum %>%
  filter(target == "N2" & date <= '2021-06-30') %>% 
  group_by(date,facility,target,biological_replicate) %>%
  summarize(contains_detection = all(nondetect == "detect" & ct_lod == "detectable")) %>% 
  filter(contains_detection == "TRUE") %>% 
  nrow()
```

### Y2

```{r}
#count number of total n2 biological replicates
total_bio_reps_n2_y2 <- cq_unsum %>% 
  filter(target == "N2" & date > '2021-06-30') %>% 
  group_by(date,facility,target,biological_replicate)

print(n_groups(total_bio_reps_n2_y2))

#count number of biological replicates with at least one detectable reaction
contains_detection_n2_y2 <- cq_unsum %>%
  filter(target == "N2" & date > '2021-06-30') %>% 
  group_by(date,facility,target,biological_replicate) %>%
  summarize(contains_detection = any(nondetect == "detect" & ct_lod == "detectable"))

total_detections_n2_y2 <- contains_detection_n2_y2 %>% 
  filter(contains_detection == "TRUE") %>% 
  nrow()

print(total_detections_n2_y2)

#calculate total detection rate
total_detection_freq_n2_y2 <- 
  total_detections_n2_y2/n_groups(total_bio_reps_n2_y2)

print(total_detection_freq_n2_y2)

#count number of reps with all detectable reactions
cq_unsum %>%
  filter(target == "N2" & date > '2021-06-30') %>% 
  group_by(date,facility,target,biological_replicate) %>%
  summarize(contains_detection = all(nondetect == "detect" & ct_lod == "detectable")) %>% 
  filter(contains_detection == "TRUE") %>% 
  nrow()
```

## Quantifiable detections

```{r}
#count number of biological replicates with quantifiable detections
is_quantifiable <- cq_unsum %>%
  group_by(date,facility,target,biological_replicate) %>%
  summarize(is_quantifiable = any(ct_loq == "quantifiable" & nondetect == "detect"))

total_quant <- is_quantifiable %>% 
  filter(is_quantifiable == "TRUE") %>% 
  nrow()

print(total_quant)
```

## Non-quantifiable reactions

```{r}
(6868-total_quant)/6868
```

## All 3 tech reps positive

```{r}
all_pos <- cq_unsum %>%
  group_by(date,facility,target,biological_replicate) %>%
  summarize(is_quantifiable = all(ct_loq == "quantifiable" & nondetect == "detect")) %>% 
  filter(is_quantifiable == "TRUE") %>% 
  nrow()

(4366-all_pos)/6868
```

## Quantifiable detections N1

```{r}
#count number of biological replicates with quantifiable detections
is_quantifiable_n1 <- total_bio_reps_n1 %>%
  summarize(is_quantifiable = any(ct_loq == "quantifiable" & nondetect == "detect"))

total_quant_n1 <- is_quantifiable_n1 %>% 
  filter(is_quantifiable == "TRUE") %>% 
  nrow()

print(total_quant_n1)
```

### Y1

```{r}
#count number of biological replicates with quantifiable detections
is_quantifiable_n1_y1 <- total_bio_reps_n1_y1 %>%
  summarize(is_quantifiable = any(ct_loq == "quantifiable" & nondetect == "detect"))

total_quant_n1_y1 <- is_quantifiable_n1_y1 %>% 
  filter(is_quantifiable == "TRUE") %>% 
  nrow()

print(total_quant_n1_y1)

#count number of reps with all quantifiable detections
total_bio_reps_n1_y1 %>%
  summarize(is_quantifiable = all(ct_loq == "quantifiable" & nondetect == "detect")) %>% 
  filter(is_quantifiable == "TRUE") %>% 
  nrow()
```

### Y2

```{r}
#count number of biological replicates with quantifiable detections
is_quantifiable_n1_y2 <- total_bio_reps_n1_y2 %>%
  summarize(is_quantifiable = any(ct_loq == "quantifiable" & nondetect == "detect"))

total_quant_n1_y2 <- is_quantifiable_n1_y2 %>% 
  filter(is_quantifiable == "TRUE") %>% 
  nrow()

print(total_quant_n1_y2)

#count number of reps with all quantifiable detections
total_bio_reps_n1_y2 %>%
  summarize(is_quantifiable = all(ct_loq == "quantifiable" & nondetect == "detect")) %>% 
  filter(is_quantifiable == "TRUE") %>% 
  nrow()
```

## Quantifiable detections N2

```{r}
#count number of biological replicates with quantifiable detections
is_quantifiable_n2 <- total_bio_reps_n2 %>%
  summarize(is_quantifiable = any(ct_loq == "quantifiable" & nondetect == "detect"))

total_quant_n2 <- is_quantifiable_n2 %>% 
  filter(is_quantifiable == "TRUE") %>% 
  nrow()

print(total_quant_n2)
```

### Y1

```{r}
#count number of biological replicates with quantifiable detections
is_quantifiable_n2_y1 <- total_bio_reps_n2_y1 %>%
  summarize(is_quantifiable = any(ct_loq == "quantifiable" & nondetect == "detect"))

total_quant_n2_y1 <- is_quantifiable_n2_y1 %>% 
  filter(is_quantifiable == "TRUE") %>% 
  nrow()

print(total_quant_n2_y1)

#count number of reps with all quantifiable detections
total_bio_reps_n2_y1 %>%
  summarize(is_quantifiable = all(ct_loq == "quantifiable" & nondetect == "detect")) %>% 
  filter(is_quantifiable == "TRUE") %>% 
  nrow()
```

### Y2

```{r}
#count number of biological replicates with quantifiable detections
is_quantifiable_n2_y2 <- total_bio_reps_n2_y2 %>%
  summarize(is_quantifiable = any(ct_loq == "quantifiable" & nondetect == "detect"))

total_quant_n2_y2 <- is_quantifiable_n2_y2 %>% 
  filter(is_quantifiable == "TRUE") %>% 
  nrow()

print(total_quant_n2_y2)

#count number of reps with all quantifiable detections
total_bio_reps_n2_y2 %>%
  summarize(is_quantifiable = all(ct_loq == "quantifiable" & nondetect == "detect")) %>% 
  filter(is_quantifiable == "TRUE") %>% 
  nrow()
```

## Highest copies/uL

```{r}
cq_unsum %>% 
  group_by(date,facility,target,biological_replicate) %>% 
  summarise(avg_cp_L = mean(copy_num_L),
            avg_cq = mean(ct)) %>% 
  arrange(desc(avg_cp_L))
```

## Highest viral load

```{r}
cq_unsum %>% 
  group_by(date,facility,target) %>% 
  summarise(avg_vl = exp(mean(log(viral_load)))) %>% 
  filter(target == "N2") %>% 
  arrange(desc(avg_vl))
  #arrange(avg_vl)
```

## Highest detection freq

```{r}
detection_freq_unsum %>% 
  arrange(desc(pos_rate))
```

## Cq ranges

```{r}
#N1 year 1
cq_high_y1_n1 <- cq_unsum %>% 
  filter(target == "N1" & date <= '2021-06-30') %>% 
  arrange(desc(ct)) %>% 
  head(1)

cq_low_y1_n1 <- cq_unsum %>% 
  filter(target == "N1" & date <= '2021-06-30') %>% 
  arrange(ct) %>% 
  head(1)

#N1 year 2
cq_high_y2_n1 <- cq_unsum %>% 
  filter(target == "N1" & date >= '2021-06-30') %>% 
  arrange(desc(ct)) %>% 
  head(1)

cq_low_y2_n1 <- cq_unsum %>% 
  filter(target == "N1" & date >= '2021-06-30') %>% 
  arrange(ct) %>% 
  head(1)

#N2 year 1
cq_high_y1_n2 <- cq_unsum %>% 
  filter(target == "N2" & date <= '2021-06-30') %>% 
  arrange(desc(ct)) %>% 
  head(1)

cq_low_y1_n2 <- cq_unsum %>% 
  filter(target == "N2" & date <= '2021-06-30') %>% 
  arrange(ct) %>% 
  head(1)

#N2 year 2
cq_high_y2_n2 <- cq_unsum %>% 
  filter(target == "N2" & date >= '2021-06-30') %>% 
  arrange(desc(ct)) %>% 
  head(1)

cq_low_y2_n2 <- cq_unsum %>% 
  filter(target == "N2" & date >= '2021-06-30') %>% 
  arrange(ct) %>% 
  head(1)
```

# Final summaries

```{r}
#how many total samples/bio reps were tested?
print(paste("Total reactions ran:", total_bio_reps))

#how many bio reps were N1?
print(paste("Total N1 reactions ran:", n_groups(total_bio_reps_n1)))

#how many bio reps were N2?
print(paste("Total N2 reactions ran:", n_groups(total_bio_reps_n2)))

#how many total reactions were positive?
print(paste("Total positive reactions:", total_detections)) 

#how many total reactions were negative?
print(paste("Total negative reactions:", total_nondetections))

#what is the rate of positive reactions?
print(paste("Total positive detection rate:", total_detection_freq))

#how many total N1 reactions were positive?
print(paste("Total positive N1 reactions:", total_detections_n1))

#what is the rate of positive N1 reactions?
print(paste("Total positive N1 detection rate:", total_detection_freq_n1))

#how many total N2 reactions were positive?
print(paste("Total positive N2 reactions:", total_detections_n2))

#what is the rate of positive N2 reactions?
print(paste("Total positive N2 detection rate:", total_detection_freq_n2))

#how many total reactions were quantifiable?
print(paste("Total quantifiable reactions:", total_quant))

#what is the rate of quantifiable reactions out of detectable reactions?
print(paste("Rate of quantifiable reactions out of total detected:", total_quant/total_detections))

#how many total N1 reactions were quantifiable?
print(paste("Total quantifiable N1 reactions:", total_quant_n1))

#how many total N2 reactions were quantifiable?
print(paste("Total quantifiable N2 reactions:", total_quant_n2))

#what is the rate of quantifiable reactions for N1?
print(paste("Rate of N1 quantifiable reactions:", total_quant_n1/total_detections_n1))

#what is the rate of quantifiable reactions for N2?
print(paste("Rate of N2 quantifiable reactions:", total_quant_n2/total_detections_n2))
```

```{r}
print(paste("Year 1 N1 Cq values range from",round(cq_low_y1_n1$ct,2),"to",round(cq_high_y1_n1$ct,2)))

print(paste("Year 2 N1 Cq values range from",round(cq_low_y2_n1$ct,2),"to",round(cq_high_y2_n1$ct,2)))

print(paste("Year 1 N2 Cq values range from",round(cq_low_y1_n2$ct,2),"to",round(cq_high_y1_n2$ct,2)))

print(paste("Year 2 N2 Cq values range from",round(cq_low_y2_n2$ct,2),"to",round(cq_high_y2_n2$ct,2)))
```

# Stats

## Cq

```{r}
#Year 1
y1_cq <- cq_unsum %>% filter(nondetect == "detect",
                    date <= '2021-06-30') %>% 
  select(target,ct) %>% 
  mutate(year = "Y1")
  
#Year 2
y2_cq <- cq_unsum %>% filter(nondetect == "detect",
                    date >= '2021-06-30') %>% 
  select(target,ct) %>% 
  mutate(year = "Y2")
  
cq_summary <- rbind(y1_cq,y2_cq) %>% 
  group_by(year,target) %>% 
  summarise(Mean = mean(ct),
            Median = median(ct),
            SD = sd(ct),
            Min = min(ct),
            Max = max(ct))

write_csv(cq_summary, 
          here("data/processed_data/wastewater/cq_summary_stats.csv"))
```

## DF & VL

```{r}
weekly_long <- full_join(viral_load_sum_weekly,detection_freq_sum,
                     by = "week") %>% 
  select(!"week") %>% 
  rename("WRFA N1 VL" = A_N1,
         "WRFA N2 VL" = A_N2,
         "WRFB N1 VL" = B_N1,
         "WRFB N2 VL" = B_N2,
         "WRFC N1 VL" = C_N1,
         "WRFC N2 VL" = C_N2,
         "WRFA N1 DF" = A_N1_POS,
         "WRFA N2 DF" = A_N2_POS,
         "WRFB N1 DF" = B_N1_POS,
         "WRFB N2 DF" = B_N2_POS,
         "WRFC N1 DF" = C_N1_POS,
         "WRFC N2 DF" = C_N2_POS) %>% 
  pivot_longer(cols = c("WRFA N1 VL",
         "WRFA N2 VL",
         "WRFB N1 VL",
         "WRFB N2 VL",
         "WRFC N1 VL",
         "WRFC N2 VL",
         "WRFA N1 DF",
         "WRFA N2 DF",
         "WRFB N1 DF",
         "WRFB N2 DF",
         "WRFC N1 DF",
         "WRFC N2 DF"),
         names_to = "Wastewater Metric")

summary <- weekly_long %>% drop_na() %>% 
  group_by(`Wastewater Metric`) %>% 
  summarise(Mean = mean(value),
            Median = median(value),
            SD = sd(value),
            Min = min(value),
            Max = max(value))

write_csv(summary, here("data/processed_data/wastewater/summary_stats.csv"))
```

# Visualize

```{r}
qpcr_periods <- data.frame(start = as.Date(c("2020-06-28", "2021-07-04")),
                           end = as.Date(c("2021-06-27", "2023-01-01")),
                           instrument = c("Year 1","Year 2+"))

viral_load <- viral_load_sum_weekly %>% 
  pivot_longer(cols = 2:7) %>% 
  drop_na() %>% 
  group_by(week) %>% 
  summarise(mean = exp(mean(log(value)))) %>% 
  mutate(date = as.Date(week)) %>% 
  mutate('RT-qPCR' = if_else(date > "2021-06-29","year 2+","year 1")) %>% 
  ggplot(aes(week,mean)) +
  geom_point(aes(shape = `RT-qPCR`), color = "#2171B5", size = 3) +
  geom_line(alpha = .6, color = "#2171B5", linewidth = 2) +
  geom_vline(xintercept = 18974,linetype = 2, size = .8) +
  ylab("Viral load") +
  xlab("") +
  scale_y_log10() +
  ggthemes::theme_clean() +
    scale_x_yearweek(date_breaks = "3 months",
                   date_labels = "%b '%y") +
  theme(axis.text.x = element_text(angle = 15,
                                   hjust = .9,
                                   size = 12),
        axis.text.y = element_text(size = 12,
                                   angle = 15), 
        axis.title.y = element_text(size = 14),
        legend.position = c(0.85, 0.85),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.margin = margin(1,1,1,1),
        legend.direction = "horizontal") 

viral_load

ggsave(here("figures/timeseries/log10_viral_load.png"))
```

```{r}
detection_freq <- detection_freq_sum %>% 
  pivot_longer(cols = 2:7) %>% 
  drop_na() %>% 
  group_by(week) %>% 
  summarise(mean = mean(value)) %>% 
  mutate(date = as.Date(week)) %>% 
  mutate('RT-qPCR' = if_else(date > "2021-06-29","year 2+","year 1")) %>% 
  ggplot(aes(week,mean)) +
  geom_point(aes(shape = `RT-qPCR`), color = "#08306B", size = 3) +
  geom_line(alpha = .6, color = "#08306B", linewidth = 2) +
  geom_vline(xintercept = 18974,linetype = 2, size = .8) +
  ylab("Detection freq.") +
  xlab("") +
  ggthemes::theme_clean() +
      scale_x_yearweek(date_breaks = "3 months",
                   date_labels = "%b '%y") +
  theme(axis.text.x = element_text(angle = 15,
                                   hjust = .9,
                                   size = 12),
        axis.text.y = element_text(angle = 15,
                                   size = 12),
        axis.title.y = element_text(size = 14),
        legend.position = c(0.85,0.15),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.margin = margin(1,1,1,1),
        legend.direction = "horizontal")

detection_freq

ggsave(here("figures/timeseries/detection_frequency.png"))
```

## Combine figures

```{r}
wastewater_fig <- ggarrange(viral_load,detection_freq,
          labels = c("c","d"),
          nrow = 2,
          ncol = 1)

ggsave(here("figures/timeseries/wastewater_combined.png"),
       width = 9,
       height = 5)
```

```{r}
ww_clinical_fig <- ggarrange(cases_reported,
                             test_admin,
                             viral_load,
                             detection_freq,
                   labels = "auto",
                   label.y = 0.2,
                   label.x = 0.01,
                   nrow = 4,
                   ncol = 1)

ggsave(here("figures/timeseries/ww_clinical_combined.tiff"),
       width = 10,
       height = 10)
```
